Andres Karjus

### 2019-11-20 index.Rmd
news

If you're here about materials for an upcoming workshop: [click here](https://andreskarjus.github.io/artofthefigure/).

@@

- A number of workshops in summer 2019 in various venues
- I have been developing materials on data visualization using R; these have been used during 2017-2019 in a number of different workshops for humanities and social science audiences, collectively under the name of [_aRt of the Figure_](https://andreskarjus.github.io/artofthefigure/). All the materials are [open source](https://andreskarjus.github.io/artofthefigure/).
- [I am available for booking](http://writingcentre.ppls.ed.ac.uk/appointments/) year around as a written communication consultant via the Edinburgh University School of Psychology, Philosophy and Language Sciences Writing Centre - specializing in writing about and presenting (graphs and figures of) data and data analysis results. This service is available to students of the School only. To book, go to the [appointments](http://writingcentre.ppls.ed.ac.uk/appointments/) page > Book an appointment > look for my name in the list of tutors in the 'Select staff' dropdown menu.
- I am also engaged in teaching stats and R to [Edinburgh Uni psychology](https://www.ed.ac.uk/ppls/psychology) masters students (since 2017).

**Past**

- Data visualization with R for corpus linguists, an aRt of the Figure workshop for Corpus Linguistics in Scotland network (12.04.2019)
- The aRt of the Figure, interactive plots edition, at the CLE PhD retreat 2019
- The aRt of the Figure workshop as a full day session at the [Scottish Graduate School of Social Science Summer School 2018](http://www.socsciscotland.ac.uk/skills_and_training/summer_school).
- I was working with the PPLS Writing Centre in the summer of 2018 to provide a drop-in quantitative research help service for PPLS MSc students working on their theses.
- PPLS Writing Centre short 1h/2h workshops on data visualization using R.
- aRt of the Figure as an afternoon workshop for the annual Edinburgh Linguistics Firbush retreat, spring 2018.
- Developed and co-taught a course on data analysis for digital humanities at the University of Tartu in the spring of 2016.
- Corpus linguistics using R course for the [Academia Salensis](http://academiasalensis.org) summer school of 2015.
- Assistant for courses on language technology and artificial intelligence, Department of Computer Science, University of Tartu, 2014-2016.
<br><br>

@@

- In 2018-2019 I'm helping my supervisor Prof. Kenny Smith carry out occasional language evolution workshops in primary schools around Edinburgh and Lothian.
- Entered [a video](https://www.youtube.com/watch?v=t8InfFEIINc) to Science Magazine's 11th [Dance Your Ph.D contest](https://www.sciencemag.org/projects/dance-your-phd). The idea is to explain your research topic to the general public though interpretive dance. We didn't win but it was a fun one to do!
- Co-organized the bimonthly [Edinburgh Language Lunch](http://groups.inf.ed.ac.uk/langlunch/) during 2016-2018. 
- Co-organized the [Linguistics and English Language Postgraduate Conference](http://www.lel.ed.ac.uk/~pgc/) of 2017 in Edinburgh, the [Why Linguistics Conference](http://whylinguistics.ut.ee) (2015) and the [Graduate Conference on Areal Linguistics, Grammar and Contacts](http://arealling.ut.ee) (2012) in Tartu, Estonia.

@@

Besides research and teaching and consulting and whatnot, I (fortunately) also do other things, which currently mostly consist of dance (lindy hop, salsa, bachata), jazz, outdoorsy stuff (cycling, hillwalking), boardgames, and various other things. I also blog about the wonderful oddities of life abroad (but it's all in [untranslatable](http://postkaartkaledooniast.blogspot.com) Estonian).

>>>>

If you're here about materials for an upcoming dataviz workshop: [click here](https://andreskarjus.github.io/artofthefigure/) to go to the dedicated workshops page.

@@

- I have been developing materials on data visualization using R; these have been used since 2017 in a number of different workshops for humanities and social science audiences, collectively under the name of [_aRt of the Figure_](https://andreskarjus.github.io/artofthefigure/). All the materials are [open source](https://andreskarjus.github.io/artofthefigure/).
- [I am available for booking](http://writingcentre.ppls.ed.ac.uk/appointments/) year around as a written communication consultant via the Edinburgh University School of Psychology, Philosophy and Language Sciences Writing Centre - specializing in writing about and presenting (graphs and figures of) data and data analysis results. This service is available to students of the School only. To book, go to the [appointments](http://writingcentre.ppls.ed.ac.uk/appointments/) page > Book an appointment > look for my name in the list of tutors in the 'Select staff' dropdown menu.
- I am also engaged in teaching stats and R to [Edinburgh Uni psychology](https://www.ed.ac.uk/ppls/psychology) masters students (since 2017).

**Past workshops**

- Since 2017, I've taught over a dozen workshops on R and data visualization. Some of these have been standalone events, some have been part of conferences, summer schools or academic retreats. The length is usually half a day or an entire day. See [here](https://andreskarjus.github.io/artofthefigure/) for the full list of past (and upcoming) workshops.

**Past teaching positions**

- Developed and co-taught a course on data analysis for digital humanities at the University of Tartu in the spring of 2016.
- Invited lecturer, corpus linguistics using R course for the [Academia Salensis](http://academiasalensis.org) summer school of 2015.
- Assistant for courses on language technology and artificial intelligence, Department of Computer Science, University of Tartu, 2014-2016.
<br><br>

@@

- I've been helping my supervisor Prof. Kenny Smith carry out occasional language evolution workshops in primary schools around Edinburgh and Lothian, in 2018/2019 and 2019/2020.
- Entered [a video](https://www.youtube.com/watch?v=t8InfFEIINc) to Science Magazine's 11th [Dance Your Ph.D contest](https://www.sciencemag.org/projects/dance-your-phd). The idea is to explain your research topic to the general public though interpretive dance. We didn't win but it was a fun one to do!
- Co-organized the bimonthly [Edinburgh Language Lunch](http://groups.inf.ed.ac.uk/langlunch/) during 2016-2018. 
- Co-organized the [Linguistics and English Language Postgraduate Conference](http://www.lel.ed.ac.uk/~pgc/) of 2017 in Edinburgh, the [Why Linguistics Conference](http://whylinguistics.ut.ee) (2015) and the [Graduate Conference on Areal Linguistics, Grammar and Contacts](http://arealling.ut.ee) (2012) in Tartu, Estonia.

@@

Besides research and teaching and consulting and whatnot, I (fortunately) also do other things, which currently mostly consist of dance (lindy hop, salsa, bachata), jazz, outdoorsy stuff (cycling, hillwalking), boardgames, and various other things.
